Consistency scores in text data

### 2020-08-06 outputs/documents/paper.Rmd
Expand on Tau example

**(Ke-Li add brief write-up of implementation in R please. Probably quanteda unless there's a better option.)**
To implement the n-gram model, we used the Text Analysis Utilities (tau) R package to tokenize the training corpus (citation('tau')). To ensure that the three-word sequences are split within a sentence, we split the corpus into sentences by period, exponential mark, or question marks. We then manually added an end of sentence token $<s>$ to the end of each sentence. We used the textcnt() function turn the training corpus into tri-grams, and the function outputs a textcnt object that resembles a table object that has contains the tri-grams and their counts. We then removed all the tri-grams that contains an end-of-sentence token, so the tri-grams that include a word from a new sentence will be removed. For example, the tri-gram "day </s> we" will be removed because it has words from two different sentences. The following is the sample output that show the first 4 tokens:

```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- " 
| there was no  | a rain so | a walk that | an hour in  | 
|---------------|-----------|-------------|-------------|
| 2             | 1         | 1           | 1           |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```
We can then access the tri-grams by calling the names of the object and use their counts to proceed to probability calculation. In calculating the probability of the tri-grams, we applied Kneser–Ney smoothing, the smoothing technique recommended by @chen1999empirical to improve the accuracy of n-gram models **(This function is written manually, but it's not my own code. I am reading about the Kneser–Ney smoothing to understand the math, will replace the function afterwards)**. Finally, we create a data table that contains the first two words and the last of each tri-gram in separate column and the smoothed probability in another column. The example row of the table is the following:

>>>>

There are a variety of ways to implement an n-gram model within R @citeR including **X, Y and Z**. We used the Text Analysis Utilities, `tau`, R package @citetau because of **X, Y, and Z**. To illustrate the use of `tau`, we will first install and load the library, and create a small corpus.

```{r, eval = FALSE}
install.packages("tau")
```

```{r}
library(tau)
corpus <- "There was no possibility of taking a walk that day. We had been wandering, indeed, in the leafless shrubbery an hour in the morning; but since dinner (Mrs. Reed, when there was no company, dined early) the cold winter wind had brought with it clouds so sombre, and a rain so penetrating, that further out-door exercise was now out of the question."
```

Our purpose is to construct tri-grams and so we first split the corpus into sentences by period, exponential mark, or question marks. We then manually added an end of sentence token $<s>$ to the end of each sentence.

```{r}
# Add simple code for however this is done in tua?
```

Next we remove all punctuation and other non-letter characters, and convert all text to lower case.

```{r}
# Add however this is done in tua?
```

We will use the `textcnt()` function to turn the training corpus into tri-grams. The most important argument of this function is the corpus, as well as **X, Y and Z**.  The function outputs a `textcnt` object, which is essentially a table with each tri-gram and their counts.

```{r}
# Add code to do this in tau
```

At this point it is possible to take other measures around fine-tuning the tri-grams. For instance we may like to remove the tri-grams that contain an end-of-sentence token. This would mean that tri-grams that include a word from a new sentence will be removed. For example, the tri-gram 'day </s> we' will be removed because it has words from two different sentences. Table **X** shows the the first four tri-grams from the small sample corpus after this process.

```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| there was no  | a rain so | a walk that | an hour in  |
|---------------|-----------|-------------|-------------|
| 2             | 1         | 1           | 1           |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```
The tri-grams can be accessed by calling the names of this table object and the counts can be used to calculate probabilities. There are a variety of options around constructing these probabilities. One is Kneser–Ney smoothing, which is the smoothing technique recommended by @chen1999empirical to improve the accuracy of n-gram models **(This function is written manually, but it’s not my own code. I am reading about the Kneser–Ney smoothing to understand the math, will replace the function afterwards)**.

Finally, it is helpful to create a data table that contains the first two words and the last of each tri-gram in separate column and the smoothed probability in another column. For instance, Table **X** provides and example of this set-up.
